---
title: "PEDSnet & TriNetX Combined Output"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_collapsed: yes
    toc_float: yes
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, 
  output_file = paste0('combined_network_output_', format(Sys.time(), '%Y%m%d'), '.html') )})
---

```{r setup, include=FALSE}
# Default taken from R notebook behavior: when knitting, wd will always be location of notebook
base_dir <- '..'
Sys.setenv(PEDSNET_SKIP_REQUEST_EXECUTION=1)
tryCatch(source('../site/run.R'),
         error = function (e) message(e)) # May not be able to make db connection

# Set to "local" to read data from ../results, or another value to read from db
data_source <- if_else(config('execution_mode') == 'distribution', 'local', 'not_local')

require(tidyr)
require(knitr)
require(kableExtra)
require(stringr)
require(tibble)
require(ggplot2)
require(ggiraph)
require(plotly)

get_results <- function(tbl_name) {
  if (data_source == 'local') {
    rslt <- read_csv(paste0('../results/', tbl_name, '.csv'))
  }
  else {
    rslt <- results_tbl(tbl_name) %>% collect()
  }
rslt
}

prettify_kable <- function(data) {
  rslt <- data %>% kable(digits = 4, format.args = list(big.mark = ','))
  if (knitr::is_html_output()) rslt <- rslt %>%
    kable_styling(bootstrap_options = c("striped", "hover")) %>%
    column_spec(1, bold = T, border_right = T)
  rslt
}

case_mix_df <- read_csv(file = '../results/COMBINED_case_mix.csv')

opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```

## Couplets
```{r cplt_exp}

#' Cohort Overlap of Both Cohorts
couplets_prop_combined <- 
  ms_exp_nt(read_csv(file = '../results/COMBINED_couplets.csv') %>% filter(cohort=='combined') %>% 
              filter(! str_detect(site_anon,'all|ALL')), 'prop') +
  ggtitle('Proportion of Combined Over Total in Both')

couplets_prop_combined

#' Proportion of Patients in Cohort 2 who are in Cohort 1
couplets_prop_cohort_1 <- 
  ms_exp_nt(read_csv(file = '../results/COMBINED_couplets.csv') %>% filter(cohort=='cohort_1_denom_prop') %>% 
              filter(! str_detect(site_anon,'all|ALL')), 'prop') +
  ggtitle('Proportion of Cohort 2 in Cohort 1')

couplets_prop_cohort_1

```

#### Anomaly Detection (TriNetX sites only)

```{r cplt_anom}

couplet_anomaly_plot_trinetx <- ms_anom_nt(process_output=
                                             read_csv(file = '../results/COMBINED_couplets_anom.csv') %>% 
                                             filter(site %in% c('HCO1','HCO2','HCO3',
                                                                'HCO4','HCO5','HCO6',
                                                                'HCO7','HCO8','HCO9','HCO10',
                                                                'HCO11','HCO12','HCO13')),
                                           comparison_col='prop',
                                           variable='couplet_name')

couplet_anomaly_plot_trinetx

```

## Signatures / Case-Mix

```{r mix}

casemix_output <- ms_exp_nt2(process_output = read_csv(file = '../results/COMBINED_case_mix.csv') %>%
                               filter(cohort == 'full'),
                             check_string = 'Branch',
                             y_col = 'branch',
                             descriptor_col = 'description')

casemix_output 

```

### Comparing Both Networks

```{r mix2}

  casemix_twosites_tbl <- read_csv(file = '../results/COMBINED_case_mix.csv') %>% 
                          mutate(site_assignment = 
                                   case_when(
                                     site_anon %in% c('HCO1','HCO2','HCO3',
                                                      'HCO4','HCO5','HCO6',
                                                      'HCO7','HCO8','HCO9',
                                                      'HCO10','HCO11','HCO12','HCO13') ~ 'Trinetx',
                                     TRUE ~ 'PEDSnet'
                                   )) %>% 
                           rename(site_original=site_anon,
                                  site_anon=site_assignment) %>% filter(cohort == 'full')
  
  casemix_output_twosites <- ms_exp_nt2(process_output=casemix_twosites_tbl,
                                        check_string = 'Branch',
                                        y_col = 'branch',
                                        descriptor_col = 'description')
  
  casemix_twocats_tbl <- casemix_twosites_tbl %>% 
                         rename(site_category=site_anon,
                                site_anon=site_original)
  
  casemix_output_twocats <- ms_exp_nt2_facet(process_output=casemix_twocats_tbl,
                                       check_string = 'Branch',
                                       y_col = 'branch',
                                       descriptor_col = 'description') 
  casemix_output_twocats

```

### SCD
``` {r mix_scd}

casemix_output_scd <- ms_exp_nt2(process_output = case_mix_df %>% filter(cohort=='scd'),
                             check_string = 'Branch',
                             y_col = 'branch',
                             descriptor_col = 'description')
casemix_output_scd
```

### SCD P-Chapter

``` {r mix_scd_p_graph}

casemix_output_scd_p <- ms_exp_nt2(process_output = case_mix_df %>% filter(cohort=='scd_p'),
                                   check_string = 'Branch',
                                   y_col = 'branch',
                                   descriptor_col = 'description')
casemix_output_scd_p
```

### Metformin

``` {r mix_metformin}
casemix_output_metformin <- ms_exp_nt2(process_output = case_mix_df %>% filter(cohort=='metformin'),
                                 check_string = 'Branch',
                                 y_col = 'branch',
                                 descriptor_col = 'description')

casemix_output_metformin

```

### SCD and Metformin
``` {r mix_scd_metformin}
casemix_output_scd_metformin <- ms_exp_nt2_facet(process_output=case_mix_df %>% filter(cohort %in% c('scd','metformin')),
                                                 check_string = 'Branch',
                                                 y_col = 'branch',
                                                 descriptor_col = 'description',
                                                 facet_wrap_var = 'cohort') 
casemix_output_scd_metformin

```



### PEDSnet Anomaly Detection

```{r mix_anon}

#' Setting up for Anomaly Detection
casemix_anomaly_cohort <- compute_dist_anomalies(df_tbl= 
                                            read_csv(file = '../results/COMBINED_case_mix.csv') %>%
                                              rename(site=site_anon) %>% filter(cohort == 'full'), 
                                                   grp_vars=c('branch','description','allsite_median'),
                                                   var_col='prop_pts')
casemix_anomaly_final_cohort <- detect_outliers(casemix_anomaly_cohort,
                                                  column_analysis='prop_pts',
                                                  column_variable = 'branch')

casemix_anomaly_plot_combined <- ms_anom_nt(process_output=casemix_anomaly_final_cohort,
                                            comparison_col='prop_pts',variable='branch')

casemix_anomaly_plot_combined

#' PEDSnet Only 
#' 
casemix_anomaly_cohort_pedsnet <- compute_dist_anomalies(df_tbl=casemix_twocats_tbl %>% 
                                                           filter(site_category == 'PEDSnet') %>% 
                                                   rename(site=site_anon), 
                                                 grp_vars=c('branch','description','allsite_median'),
                                                 var_col='prop_pts')

casemix_anomaly_final_cohort_pedsnet <- detect_outliers(casemix_anomaly_cohort_pedsnet,
                                                column_analysis='prop_pts',
                                                column_variable = 'branch')

casemix_anomaly_plot_combined_pedsnet <- ms_anom_nt(process_output=casemix_anomaly_final_cohort_pedsnet,
                                                    comparison_col='prop_pts',variable='branch')

casemix_anomaly_plot_combined_pedsnet

```

### TriNetX Anomaly Detection

```{r mix_anon2}

mix_anon_combo <- trinetx_anom_detect(dat = read_csv(file = '../results/COMBINED_case_mix.csv') %>%
                                              filter(cohort == 'full'),
                                      var_col = 'prop_pts',
                                      grp_vars = 'branch')

dat_to_plot <- mix_anon_combo %>%
    mutate(text=paste("Variable: ",branch,
                      "\nSite: ",site_anon,
                      "\nProportion: ",round(prop_pts,2),
                      "\nSeverity Score: ", round(severity_score, 4),
                      "\nSite Outlier Score: ", round(site_score,4)))
  
  
  #mid<-(max(dat_to_plot[[comparison_col]],na.rm=TRUE)+min(dat_to_plot[[comparison_col]],na.rm=TRUE))/2
  
  plt<-ggplot(dat_to_plot %>% filter(anomaly_yn != 'no outlier in group') %>%
                mutate(severity_score = ifelse(is.na(severity_score), 0, severity_score)),
              aes(x=site_anon, y=branch, text=text, color=prop_pts))+
    geom_point_interactive(aes(size=prop_pts,shape=anomaly_yn, tooltip = text))+
    scale_color_ssdqa(palette = 'diverging', discrete = FALSE) +
    scale_shape_manual(values=c(8,20,8))+
    #scale_y_discrete(labels = function(x) str_wrap(x, width = text_wrapping_char)) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=60)) +
    labs(y = "Branch",
         size="",
         title = 'All Sites') +
    guides(color = guide_colorbar(title = 'Proportion'),
           shape = guide_legend(title = 'Anomaly'),
           size = 'none')
  
  girafe(ggobj = plt)
  
  
  mix_anon_combo_peds <- trinetx_anom_detect(dat = read_csv(file = '../results/COMBINED_case_mix.csv') %>%
                                              filter(cohort == 'full', grepl('site', site_anon)),
                                      var_col = 'prop_pts',
                                      grp_vars = 'branch')

dat_to_plot <- mix_anon_combo_peds %>%
    mutate(text=paste("Variable: ",branch,
                      "\nSite: ",site_anon,
                      "\nProportion: ",round(prop_pts,2),
                      "\nSeverity Score: ", round(severity_score, 4),
                      "\nSite Outlier Score: ", round(site_score,4)))
  
  
  #mid<-(max(dat_to_plot[[comparison_col]],na.rm=TRUE)+min(dat_to_plot[[comparison_col]],na.rm=TRUE))/2
  
  plt<-ggplot(dat_to_plot %>% filter(anomaly_yn != 'no outlier in group') %>%
                mutate(severity_score = ifelse(is.na(severity_score), 0, severity_score)),
              aes(x=site_anon, y=branch, text=text, color=prop_pts))+
    geom_point_interactive(aes(size=prop_pts,shape=anomaly_yn, tooltip = text))+
    scale_color_ssdqa(palette = 'diverging', discrete = FALSE) +
    scale_shape_manual(values=c(8,20,8))+
    #scale_y_discrete(labels = function(x) str_wrap(x, width = text_wrapping_char)) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=60)) +
    labs(y = "Branch",
         size="",
         title = 'PEDSnet Only') +
    guides(color = guide_colorbar(title = 'Proportion'),
           shape = guide_legend(title = 'Anomaly'),
           size = 'none')
  
  girafe(ggobj = plt)


```


## Coverage Overlap

```{r cvg}

cvg_output <- ms_exp_nt2(process_output = read_csv(file = '../results/COMBINED_cvg_overlap.csv'),
                             check_string = 'Fact Group',
                             y_col = 'fact_group',
                             descriptor_col = 'fact_long')

cvg_output

```

```{r cvg2}

cvg_overlap_anom_tbl <- compute_dist_anomalies(df_tbl= read_csv(file = '../results/COMBINED_cvg_overlap.csv')
                                               %>% rename(site=site_anon), 
                                               grp_vars=c('fact_group','fact_long', 'allsite_median'),
                                               var_col='prop_pts')

cvg_overlap_anom_tbl2 <- detect_outliers(cvg_overlap_anom_tbl,
                                         column_analysis='prop_pts',
                                         column_variable = 'fact_group')

cvg_overlap_anom_plot <- ms_anom_nt(process_output=cvg_overlap_anom_tbl2,
                                    comparison_col='prop_pts',
                                    variable='fact_group')

cvg_overlap_anom_plot

```

## Stability Over Time

Here, we are using the normalized patient count computed using the heuristic developed by the PEDSnet team. This is  `month / ((month-1)*.25 + (month+1)*.25 + (month-12)*.5)`

### Combined (All Sites Included)
```{r fot}

check_type <- 'hypertension'

fot_all <- euclidean_output(process_output = read_csv('../results/FOT_combined.csv'),
                             output_var = 'check',
                             filter_variable = check_type)

fot_all[[1]]
fot_all[[2]]
fot_all[[3]]
```

### Separated (Different Graphs per Network)

```{r fot_sep}
fot_chop <- euclidean_output(process_output = read_csv('../results/FOT_chop.csv'),
                              output_var = 'check',
                              filter_variable = check_type)

fot_chop[[1]]
fot_chop[[2]]
fot_chop[[3]]


fot_tnx <- euclidean_output(process_output = read_csv('../results/FOT_trinetx.csv'),
                             output_var = 'check',
                             filter_variable = check_type)

fot_tnx[[1]]
fot_tnx[[2]]
fot_tnx[[3]]


```