---
title: "TriNetX & PEDSnet Output"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_collapsed: yes
    toc_float: yes
---

```{r setup, include=FALSE}
# Default taken from R notebook behavior: when knitting, wd will always be location of notebook
base_dir <- '..'
Sys.setenv(PEDSNET_SKIP_REQUEST_EXECUTION=1)
tryCatch(source('../site/run.R'),
         error = function (e) message(e)) # May not be able to make db connection

# Set to "local" to read data from ../results, or another value to read from db
data_source <- if_else(config('execution_mode') == 'distribution', 'local', 'not_local')

require(tidyr)
require(knitr)
require(kableExtra)
require(stringr)
require(tibble)
require(ggplot2)
require(gt)
require(timetk)

get_results <- function(tbl_name) {
  if (data_source == 'local') {
    rslt <- read_csv(paste0('../results/', tbl_name, '.csv'))
  }
  else {
    rslt <- results_tbl(tbl_name) %>% collect()
  }
rslt
}

prettify_kable <- function(data) {
  rslt <- data %>% kable(digits = 4, format.args = list(big.mark = ','))
  if (knitr::is_html_output()) rslt <- rslt %>%
    kable_styling(bootstrap_options = c("striped", "hover")) %>%
    column_spec(1, bold = T, border_right = T)
  rslt
}

site_map <- read_csv('../results/site_mapping.csv')

case_mix_df <- read_csv(file = '../results/COMBINED_case_mix.csv')

opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

fot_compute_proportions <- function(fot_tbl = fot_chop_trinetx_rawcts %>% filter(cohort=='pedsnet'),
                                    var_col = 'row_visits',
                                    denom_groups = c('all_visits'),
                                    num_groups = c('outpatient_visits')) {
  
  denom_pts <- 
    fot_tbl %>% 
    filter(check_desc %in% denom_groups) %>% 
    group_by(site_anon,
             month_end) %>% summarise(var_denom=sum(!!sym(var_col))) 
  
  
  num_pts <- 
    fot_tbl %>% 
    filter(check_desc %in% num_groups) %>% 
    group_by(site_anon,
             month_end) %>% summarise(var_num=sum(!!sym(var_col))) 
  
  num_denom_prop <- 
    denom_pts %>% 
    left_join(
      num_pts
    ) %>% 
    mutate(prop=round(var_num/var_denom, 2))
  
  
}
```

## Couplets

### Exploratory
```{r cplt_exp}

#' Cohort Overlap of Both Cohorts
# couplets_prop_combined <- 
#   couplet_viz(read_csv(file = '../results/COMBINED_couplets.csv') %>% filter(cohort=='combined') %>% 
#               filter(! str_detect(site_anon,'all|ALL')), 'prop') +
#   ggtitle('Proportion of Combined Over Total in Both')
# 
# couplets_prop_combined

#' Proportion of Patients in Cohort 2 who are in Cohort 1
couplets_prop_cohort_1 <- 
  couplets_viz(read_csv(file = '../results/COMBINED_couplets.csv') %>% filter(cohort=='cohort_1_denom_prop') %>% mutate(prop = round(prop, 2)) %>%
              filter(! str_detect(site_anon,'all|ALL')), 'prop') +
  ggtitle('Proportion of Cohort 2 in Cohort 1')

couplets_prop_cohort_1

```

### Outlier Detection

In these graphs, if the point is an outlier, the shape is a triangle (indicating directionality of the outlier) and the size indicates the severity of the outlier. If the point is NOT an outlier, the shape is a circle and the size represents the IQR value for that group. The color in all cases represents the raw proportion.


```{r cplt_anom, include=FALSE}

cplt_anom <- trinetx_anom_detect(dat = read_csv(file = '../results/COMBINED_couplets.csv') %>%
                                   filter(cohort == 'combined') %>% filter(! str_detect(site_anon,'all|ALL')) %>% mutate(prop = prop * 100, network = ifelse(grepl('HCO', site_anon), 'trinetx', 'pedsnet')),
                                 var_col = 'prop',
                                 grp_vars = c('couplet_name'))

combo <- trinetx_anom_viz(dat = cplt_anom,
                 var_col = 'prop',
                 grp_col = 'couplet_name')

combo[[1]]
combo[[2]]

```

#### Proportion of Cohort 2 in Cohort 1

##### Computing for both networks as one group

```{r cplt_anom2}
cplt_anom2 <- trinetx_anom_detect(dat = read_csv(file = '../results/COMBINED_couplets.csv') %>%
                                   filter(cohort == 'cohort_1_denom_prop') %>% filter(! str_detect(site_anon,'all|ALL'), !is.na(prop)) %>%
                                    mutate(prop = prop * 100,
                                           network = ifelse(grepl('HCO', site_anon),
                                                            'trinetx', 'pedsnet')),
                                 var_col = 'prop',
                                 grp_vars = c('couplet_name'))

c1_denom <- trinetx_anom_viz(dat = cplt_anom2,
                 var_col = 'prop',
                 grp_col = 'couplet_name')

c1_denom[[1]]
c1_denom[[2]]

```

##### Computing for both networks individually

```{r cplt_anom2.1}
cplt_anom2 <- trinetx_anom_detect(dat = read_csv(file = '../results/COMBINED_couplets.csv') %>%
                                   filter(cohort == 'cohort_1_denom_prop') %>% filter(! str_detect(site_anon,'all|ALL'), !is.na(prop)) %>%
                                    mutate(prop = prop * 100,
                                           network = ifelse(grepl('HCO', site_anon),
                                                            'trinetx', 'pedsnet')),
                                 var_col = 'prop',
                                 grp_vars = c('couplet_name', 'network'))

c1_denom <- trinetx_anom_viz(dat = cplt_anom2,
                 var_col = 'prop',
                 grp_col = 'couplet_name')

c1_denom[[1]]
c1_denom[[2]]

```


```{r test, include=FALSE}

couplet_anomaly_plot_trinetx <- ms_anom_nt(process_output=
                                             read_csv(file  = '../results/COMBINED_couplets_anom.csv'),
                                           comparison_col='prop',
                                           variable='couplet_name')

couplet_anomaly_plot_trinetx


```


```{r test2, include=FALSE}

couplet_anomaly_plot_trinetx <- ms_anom_nt(process_output=
                                             read_csv(file  = '../results/TRINETX_couplets_anom.csv') %>% union(read_csv(file  = '../results/PEDSNET_couplets_anom.csv')),
                                           comparison_col='prop',
                                           variable='couplet_name')

couplet_anomaly_plot_trinetx


```

## Coverage Overlap

### Exploratory
```{r cvg_exp, fig.height=7}

cvg_output <- coverage_overlap_viz(process_output = 
                                     read_csv(file = '../results/COMBINED_cvg_overlap.csv'))

cvg_output

```

### Outlier Detection
```{r cvg_anom}

cvg_anom <- trinetx_anom_detect(dat = read_csv(file = '../results/COMBINED_cvg_overlap.csv') %>%
                                  mutate(prop_pts = prop_pts * 100,
                                           network = ifelse(grepl('HCO', site_anon),
                                                            'trinetx', 'pedsnet')),
                                var_col = 'prop_pts',
                                grp_vars = c('fact_long', 'network'))

cvg_anom_grph <- trinetx_anom_viz(dat = cvg_anom,
                                  var_col = 'prop_pts',
                                  grp_col = 'fact_long')

cvg_anom_grph[[1]]
cvg_anom_grph[[2]]

```

## Signatures / Case-Mix

### Exploratory

#### Single Site Summary

```{r mix_summ}

mix_summ <- case_mix_summ_viz(process_output = 
                                read_csv(file = '../results/COMBINED_case_mix.csv') %>%
                                filter(cohort == 'full'),
                              site_filter = 'site 2')

mix_summ


```

#### Overall

```{r mix, fig.height=10}

# casemix_output <- ms_exp_nt2(process_output = read_csv(file = '../results/COMBINED_case_mix.csv') %>%
#                                filter(cohort == 'full'),
#                              check_string = 'Branch',
#                              y_col = 'branch',
#                              descriptor_col = 'description')
# 
# casemix_output 

mix_output <- case_mix_viz(process_output = 
                             read_csv(file = '../results/COMBINED_case_mix.csv') %>%
                                filter(cohort == 'full'))

mix_output

```



```{r mix2_compare, include=FALSE}

  # casemix_twosites_tbl <- read_csv(file = '../results/COMBINED_case_mix.csv') %>% 
  #                         mutate(site_assignment = 
  #                                  case_when(
  #                                    site_anon %in% c('HCO1','HCO2','HCO3',
  #                                                     'HCO4','HCO5','HCO6',
  #                                                     'HCO7','HCO8','HCO9',
  #                                                     'HCO10','HCO11','HCO12','HCO13') ~ 'Trinetx',
  #                                    TRUE ~ 'PEDSnet'
  #                                  )) %>% 
  #                          rename(site_original=site_anon,
  #                                 site_anon=site_assignment) %>% filter(cohort == 'full')
  # 
  # casemix_output_twosites <- ms_exp_nt2(process_output=casemix_twosites_tbl,
  #                                       check_string = 'Branch',
  #                                       y_col = 'branch',
  #                                       descriptor_col = 'description')
  # 
  # casemix_twocats_tbl <- casemix_twosites_tbl %>% 
  #                        rename(site_category=site_anon,
  #                               site_anon=site_original)
  # 
  # casemix_output_twocats <- ms_exp_nt2_facet(process_output=casemix_twocats_tbl,
  #                                      check_string = 'Branch',
  #                                      y_col = 'branch',
  #                                      descriptor_col = 'description') 
  # casemix_output_twocats

```

#### SCD
``` {r mix_scd, fig.height = 10}

mix_output_scd <- case_mix_viz(process_output = 
                             read_csv(file = '../results/COMBINED_case_mix.csv') %>%
                                filter(cohort == 'scd'))

mix_output_scd
```

#### SCD: P Sub-Branch

``` {r mix_scd_p_graph, fig.height = 9}

mix_output_scdp <- case_mix_viz(process_output = 
                             read_csv(file = '../results/COMBINED_case_mix.csv') %>%
                                filter(cohort == 'scd_p'))

mix_output_scdp
```

#### With Visit Counts

```{r mix_visits, fig.height=10}

mix_pts <- read_csv(file = '../results/COMBINED_case_mix.csv') %>% filter(cohort == 'full') %>%
  filter(grepl('site', site_anon)) %>% pivot_longer(cols = 'prop_pts',
                                                    names_to = 'prop_type',
                                                    values_to = 'prop') %>%
  select(site_anon, branch, description, prop, prop_type)

descs <- mix_pts %>% distinct(branch, description)

mix_visits <- read_csv(file = '../results/case_mix_visits_chop.csv') %>%
  filter(grepl('site', site_anon)) %>% pivot_longer(cols = 'prop_visit_site',
                                                    names_to = 'prop_type',
                                                    values_to = 'prop') %>%
  rename('branch' = icd_header) %>%
  mutate(branch = str_replace_all(branch, ' ', '')) %>%
  select(site_anon, branch, prop, prop_type) %>%
  left_join(descs)

mix_both <- mix_pts %>% union(mix_visits)%>% mutate(prop_type = ifelse(grepl('pts', prop_type), 
                                                                       'Patients', 'Visits'))

case_mix_visits_viz(process_output = mix_both)

```

### Outlier Detection

#### Overall
```{r mix_anom}

mix_anon_combo <- trinetx_anom_detect(dat = read_csv(file = '../results/COMBINED_case_mix.csv') %>%
                                              filter(cohort == 'full',
                                                     !grepl('U', branch)) %>%
                                        mutate(prop_pts = prop_pts * 100,
                                           network = ifelse(grepl('HCO', site_anon),
                                                            'trinetx', 'pedsnet')),
                                      var_col = 'prop_pts',
                                      grp_vars = c('branch', 'network'))

mix_anon_graph <- trinetx_anom_viz(dat = mix_anon_combo,
                                   var_col = 'prop_pts',
                                   grp_col = 'branch')

mix_anon_graph[[1]]
mix_anon_graph[[2]]

```

#### SCD
```{r mix_anom_scd}

mix_anon_combo <- trinetx_anom_detect(dat = case_mix_df %>% filter(cohort=='scd') %>%
                                        mutate(prop_pts = prop_pts * 100,
                                               network = ifelse(grepl('HCO', site_anon),
                                                            'trinetx', 'pedsnet')),
                                      var_col = 'prop_pts',
                                      grp_vars = c('branch', 'network'))

mix_anon_graph <- trinetx_anom_viz(dat = mix_anon_combo,
                                   var_col = 'prop_pts',
                                   grp_col = 'branch')

mix_anon_graph[[1]]
mix_anon_graph[[2]]

```

## Stability Over Time

```{r fot_setup, include=FALSE}

# ## Read in data
# fot_trinetx <- read_csv('../results/factsovertime_trinetx.csv')
# fot_chop <- read_csv('../results/factsovertime_rawcts.csv') %>%
#   left_join(read_csv('../results/factsovertime_normalized.csv')) #%>%
#   #left_join(read_csv('../results/factsovertime_distance.csv'))
# fot_chop_additional <- read_csv('../results/fot_output_new_chop.csv')
# 
# ## Clean trinetx data
# fot_trinetx_clean <- fot_trinetx %>%
#   rename(check_desc = query,
#          month_end = date,
#          row_pts = patients) %>%
#   mutate(month_end = as.Date(month_end, format = '%d %b %Y')) %>%
#   mutate(check_desc = case_when(grepl('anxiety', check_desc) ~ 'anxiety',
#                                 grepl('asthma', check_desc) ~ 'asthma',
#                                 grepl('hypertension', check_desc) ~ 'hypertension',
#                                 grepl('resp', check_desc) ~ 'respiratory_infection',
#                                 grepl('emergency', check_desc) ~ 'emergency_visits',
#                                 grepl('emergency vitals', check_desc) ~ 'emergency_visit_vitals',
#                                 grepl('inpatients', check_desc) ~ 'inpatient_visits',
#                                 grepl('meds', check_desc) ~ 'inpatient_administration',
#                                 grepl('outpatients', check_desc) ~ 'outpatient_visits',
#                                 grepl('procedures', check_desc) ~ 'outpatient_procedure'))
# 
# 
# 
# ## Rerun heuristic based on patient counts to make sure both sets of output are aligned
# fot_trinetx_new <- compute_at_cross_join(cj_tbl = fot_trinetx_clean %>% 
#                                            mutate(time_start = month_end, time_increment = 'month'), 
#                                          cj_var_names = c('site_anon', 'check_desc'))
# 
# fot_list_trinetx <- fot_check('row_pts',
#                               tblx= fot_trinetx_new %>% 
#                                 filter(site_anon != 'All HCOs') %>% 
#                                 mutate(check_name = check_desc, site = site_anon))
# 
# fot_trinetx_final <- fot_list_trinetx$fot_heuristic %>% 
#   rename(site_anon = site) %>%
#   select(site_anon, month_end, check_desc, row_pts, check)
# 
# ## Clean trinetx data
# fot_chop_clean <- fot_chop %>%
#   select(site_anon, month_end, check_desc, row_pts, row_visits) %>%
#    mutate(month_end = as.Date(month_end, format = '%m/%d/%y')) %>%
#   union(fot_chop_additional %>% select(site_anon, month_end, check_desc, row_pts, row_visits))
# 
# 
# fot_chop_trinetx_rawcts <- 
#   dplyr::union(fot_trinetx_new %>% select(site_anon,month_end,check_desc,row_pts) %>%
#                  mutate(cohort='trinetx', row_visits=0),
#                fot_chop_clean %>% select(site_anon,month_end,check_desc,row_pts,row_visits) %>% 
#                  mutate(#month_end=mdy(month_end),
#                         cohort='pedsnet'))

```

### Exploratory

#### Raw & Normalized Patients

```{r fot_exp}

# fot_norm <- read_csv('../results/factsovertime_normalized.csv') %>%
#   mutate(month_end = as.Date(month_end, format = '%m/%d/%y'))

fot_combo <- read_csv('../results/COMBINED_fot.csv') %>%
  mutate(cohort = ifelse(grepl('site', site_anon), 'pedsnet', 'trinetx'))

# fot_combo <- fot_chop %>%
#   mutate(month_end = as.Date(month_end, format = '%m/%d/%y')) %>%
#   left_join(read_csv('../results/site_mapping.csv')) %>%
#   select(site_anon, month_end, check_desc, row_pts, check) %>%
#   union(fot_trinetx_final)

domain_list <- fot_combo %>% distinct(check_desc) %>% pull()
site_list <- fot_combo %>% filter(!is.na(site_anon), site_anon != 'all') %>% distinct(site_anon) %>% pull()

final <- list()

for(i in 1:length(site_list)){
  
  tbl <- fot_combo %>%
    filter(site_anon == site_list[[i]])
  
  temp <- list()
  
  for(k in 1:length(domain_list)){
    
    ay <- list(
      tickfont = list(color = "red"),
      overlaying = "y",
      side = "right",
      title = "Normalized Patients")

  plt <- tbl %>%
    filter(check_desc == domain_list[[k]]) %>%
    plot_ly() %>%
    add_lines(x = ~month_end, y = ~row_pts, yaxis = 'y1', name = 'Patients') %>%
    add_lines(x = ~month_end, y = ~check, yaxis = 'y2', name = 'Normalized Patients',
              line = list(color = 'navy', dash = 'dot')) %>%
    layout(
      title = paste0(site_list[[i]], ' ', domain_list[[k]]), 
      yaxis2 = ay,
      xaxis = list(title="Month End"),
      yaxis = list(title="Patients"))
  
  temp[[k]] <- plt
  
  }
  
  final[[i]] <- temp
}

final[[1]][[5]]
final[[22]][[10]]
final[[7]][[10]]

```

#### Incidence Rate (per 10,000 patients)
```{r fot_exp2}

fot_denoms <- fot_combo %>% 
  filter(check_desc == 'all_visits') %>% distinct(site_anon, month_end, row_pts) %>% 
  rename('total_pt' = row_pts)

fot_combo_rates <- fot_combo %>%
  mutate(new_cases = row_pts) %>%
  left_join(fot_denoms) %>%
  filter(!is.na(total_pt)) %>%
  mutate(incidence_rate = (new_cases / total_pt) * 10000)


ggplot(fot_combo_rates, aes(y = incidence_rate, x = month_end, color = site_anon)) +
  geom_line() +
  facet_wrap(~check_desc, scales = 'free_y', ncol = 2) +
  theme_minimal() +
  scale_color_ssdqa()
  

```

### Multi-Site Outlier Detection

#### Proportions - Inpatient Asthma Visits per All Inpatient Visits

```{r fot_anom1}

ip_asthma_all_visit <- fot_compute_proportions(fot_tbl = fot_combo %>% filter(cohort=='pedsnet'),
                                         var_col = 'row_visits',
                                         denom_groups = c('inpatient_visits'),
                                         num_groups = c('asthma_inpatient'))


asthma_ip_medians <- compute_dist_mean_median(ip_asthma_all_visit,
                                  c('month_end'),
                                  c('prop'),
                                  num_sd=2,
                                  num_mad=2)

asthma_ip_euclidean <- ms_anom_euclidean(fot_input_tbl = asthma_ip_medians %>% 
                                           mutate(time_start = month_end,
                                                  time_increment = 'month'),
                                            grp_vars = c('site_anon'),
                                            var_col = 'prop')

fot_asthma_ip_output <- fot_euclidean_viz(process_output = asthma_ip_euclidean,
                                             output_var = 'prop',
                                             filter_variable = NULL,
                                             title = 'Inpatient Asthma Over Time')

fot_asthma_ip_output[[1]]
fot_asthma_ip_output[[2]]
fot_asthma_ip_output[[3]]


```

#### Incidence Rate (per 10,000 patients)
```{r fot_anom2}

# rate_medians <- compute_dist_mean_median(fot_combo_rates %>% filter(check_desc == 'outpatient_visits'),
#                                         c('month_end'),
#                                         c('incidence_rate'),
#                                         num_sd=2,
#                                         num_mad=2)

rate_euclidean <- ms_anom_euclidean(fot_input_tbl = fot_combo_rates %>% 
                                      mutate(time_start = month_end,
                                             time_increment = 'month'),
                                            grp_vars = c('site_anon', 'check_desc'),
                                            var_col = 'incidence_rate')

rate_output <- fot_euclidean_viz(process_output = rate_euclidean,
                                output_var = 'incidence_rate',
                                filter_variable = 'hypertension',
                                title = 'Rate per 10,000 Patients for Hypertension Over Time')

rate_output[[1]]
rate_output[[2]]
rate_output[[3]]


```

### Single-Site Anomaly Detection

#### TriNetX Method
```{r fot_ss_anom}

fot_combo_anom <- trinetx_anom_detect(dat = fot_combo_rates,
                                      var_col = 'incidence_rate',
                                      grp_vars = c('site_anon', 'check_desc')) %>%
  inner_join(fot_combo_rates) %>%
  distinct() %>%
  filter(site_anon == 'site 10', check_desc == 'respiratory_infection')

fot_combo_anom %>%
  ggplot(aes(x = month_end, y = incidence_rate)) +
  geom_line(color = 'gray') +
  geom_point(data = fot_combo_anom %>% filter(anomaly_yn == 'not outlier'), aes(colour = incidence_rate, shape = anomaly_yn)) + 
  geom_point(data = fot_combo_anom %>% filter(anomaly_yn != 'not outlier'), aes(size = severity_score, colour = incidence_rate, shape = anomaly_yn)) +
  scale_shape_manual(values=c('upper outlier' = 24,
                              'not outlier' = 20,
                              'lower outlier' = 25)) +
  scale_color_ssdqa(discrete = FALSE, palette = 'diverging') +
  theme_minimal() +
  guides(color = guide_colorbar(title = 'Patient Count'),
         shape = guide_legend(title = 'Anomaly'),
         size = 'none') +
  labs(title = 'Anomalous Patient Counts Over Time',
       subtitle = 'Site 10; Respiratory Infections')


```

#### STL Regression (Using Incidence Rate per 10,000 Patients)

```{r fot_anom_stl}

anomalize_stl <- anomalize_ss_anom_at(fot_input_tbl = fot_combo_rates %>% 
                                             mutate(time_increment = 'month', 
                                                    time_start = month_end) %>% 
                                             filter(site_anon == 'site 10', check_desc == 'respiratory_infection') %>% distinct(), 
                                           grp_vars = 'check_desc', 
                                           time_var = 'time_start', 
                                           var_col = 'incidence_rate')

anomalize_stl_output <- ss_anom_at(process_output = anomalize_stl,
                                    filtered_var = 'respiratory_infection',
                                    var_col = 'check_desc')

anomalize_stl_output[[1]]
anomalize_stl_output[[2]]


```
