---
title: "TriNetX and PEDSnet: Stability Over Time"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_collapsed: yes
    toc_float: yes
---

```{r setup, include=FALSE}
# Default taken from R notebook behavior: when knitting, wd will always be location of notebook
base_dir <- '..'
Sys.setenv(PEDSNET_SKIP_REQUEST_EXECUTION=1)
tryCatch(source('../site/run.R'),
         error = function (e) message(e)) # May not be able to make db connection

# Set to "local" to read data from ../results, or another value to read from db
data_source <- if_else(config('execution_mode') == 'distribution', 'local', 'not_local')

require(tidyr)
require(knitr)
require(kableExtra)
require(stringr)
require(tibble)
require(ggplot2)

get_results <- function(tbl_name) {
  if (data_source == 'local') {
    rslt <- read_csv(paste0('../results/', tbl_name, '.csv'))
  }
  else {
    rslt <- results_tbl(tbl_name) %>% collect()
  }
rslt
}

prettify_kable <- function(data) {
  rslt <- data %>% kable(digits = 4, format.args = list(big.mark = ','))
  if (knitr::is_html_output()) rslt <- rslt %>%
    kable_styling(bootstrap_options = c("striped", "hover")) %>%
    column_spec(1, bold = T, border_right = T)
  rslt
}


opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```

# Single Site Exploratory Output

# Single Site Exploratory {.tabset .tabset-pills}

```{r cvg_prep}

domain_list <- read_csv('../results/COMBINED_fot.csv') %>% distinct(check_desc) %>% 
  filter(check_desc != 'all_visits', check_desc != 'asthma_inpatient') %>% pull()
site_list <- read_csv('../results/COMBINED_fot.csv') %>% 
  filter(!is.na(site_anon), site_anon != 'all') %>% 
  distinct(site_anon) %>% pull()

final <- list()

for(i in site_list){
  
  temp <- list()
  
  for(k in domain_list){
    
    dm_otpt <- fot_raw_norm_viz(process_output = read_csv('../results/COMBINED_fot.csv') %>%
                                  filter(check_desc != 'all_visits',
                                         check_desc != 'asthma_inpatient'),
                                site_filter = i,
                                domain_filter = k)
    
    temp[[k]] <- dm_otpt
  }
  
  final[[i]] <- temp
  
}


```

## Site 1

```{r}

htmltools::tagList(final[[22]])

```

## Site 2

```{r}
htmltools::tagList(final[[15]])
```

## Site 3

```{r}
htmltools::tagList(final[[17]])
```

## Site 4

```{r}
htmltools::tagList(final[[23]])
```

## Site 5

```{r}
htmltools::tagList(final[[18]])
```

## Site 6

```{r}
htmltools::tagList(final[[14]])
```

## Site 7

```{r}
htmltools::tagList(final[[21]])
```

## Site 8

```{r}
htmltools::tagList(final[[19]])
```

## Site 9

```{r}
htmltools::tagList(final[[20]])
```

## Site 10
```{r}
htmltools::tagList(final[[16]])
```

## HCO1
```{r}
htmltools::tagList(final[[1]])
```

## HCO2
```{r}
htmltools::tagList(final[[6]])
```

## HCO3
```{r}
htmltools::tagList(final[[7]])
```

## HCO4
```{r}
htmltools::tagList(final[[8]])
```

## HCO5
```{r}
htmltools::tagList(final[[9]])
```

## HCO6
```{r}
htmltools::tagList(final[[10]])
```

## HCO7
```{r}
htmltools::tagList(final[[11]])
```

## HCO8
```{r}
htmltools::tagList(final[[12]])
```

## HCO9
```{r}
htmltools::tagList(final[[13]])
```

## HCO10
```{r}
htmltools::tagList(final[[2]])
```

## HCO11
```{r}
htmltools::tagList(final[[3]])
```

## HCO12
```{r}
htmltools::tagList(final[[4]])
```

## HCO13
```{r}
htmltools::tagList(final[[5]])
```

# {-}

# Multi Site Exploratory (Incidence Rate per 10,000 Patients)
```{r}

fot_denoms <- read_csv('../results/COMBINED_fot.csv') %>% 
  filter(check_desc == 'all_visits') %>% distinct(site_anon, month_end, row_pts) %>% 
  rename('total_pt' = row_pts)

fot_tnx <- read_csv('../results/factsovertime_trinetx.csv') %>%
  select(site_anon, date, query, normalized_patients) %>%
  rename(check_desc = query,
         month_end = date) %>%
  mutate(month_end = as.Date(month_end, format = '%m/%d/%y')) %>%
  mutate(check_desc = case_when(grepl('anxiety', check_desc) ~ 'anxiety',
                                grepl('asthma', check_desc) ~ 'asthma',
                                grepl('hypertension', check_desc) ~ 'hypertension',
                                grepl('resp', check_desc) ~ 'respiratory_infection',
                                grepl('emergency$', check_desc) ~ 'emergency_visits',
                                grepl('emergency vitals', check_desc) ~
                                  'emergency_visit_vitals',
                                grepl('inpatients', check_desc) ~ 'inpatient_visits',
                                grepl('meds', check_desc) ~ 'inpatient_administration',
                                grepl('outpatients', check_desc) ~ 'outpatient_visits',
                                grepl('procedures', check_desc) ~ 'outpatient_procedure')) %>%
  mutate(incidence_rate = normalized_patients * 10000) %>%
  select(-normalized_patients)

fot_combo_rates <- read_csv('../results/COMBINED_fot.csv') %>%
  mutate(new_cases = row_pts) %>%
  left_join(fot_denoms) %>%
  filter(!is.na(total_pt)) %>%
  mutate(incidence_rate = (new_cases / total_pt) * 10000) %>%
  select(site_anon, check_desc, month_end, incidence_rate) %>%
  union(fot_tnx)


plt_list <- list()

for(p in domain_list){

    g <- ggplot(fot_combo_rates %>% filter(check_desc == p), 
           aes(y = incidence_rate, x = month_end, color = site_anon)) +
      geom_line() +
      facet_wrap(~check_desc, scales = 'free_y', ncol = 2) +
      theme_minimal() +
      scale_color_ssdqa()
    
    plt_list[[p]] <- ggplotly(g)
  
}

htmltools::tagList(plt_list)

```

# Anomaly Detection (Euclidean Distance using Incidence Rate) {.tabset .tabset-pills}

## Anxiety
```{r}

rate_euclidean <- ms_anom_euclidean(fot_input_tbl = fot_combo_rates %>% 
                                      mutate(time_start = month_end,
                                             time_increment = 'month'),
                                            grp_vars = c('site_anon', 'check_desc'),
                                            var_col = 'incidence_rate')

rate_output <- fot_euclidean_viz(process_output = rate_euclidean,
                                output_var = 'incidence_rate',
                                filter_variable = 'anxiety',
                                title = '')

sub <- subplot(rate_output[[1]], rate_output[[2]]) %>% layout(title = 'Rate per 10,000 Patients for Anxiety Over Time') %>% style(showlegend = FALSE, traces = 1:24)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
rate_output[[3]]


```

## Asthma

```{r}

rate_output <- fot_euclidean_viz(process_output = rate_euclidean,
                                output_var = 'incidence_rate',
                                filter_variable = 'asthma',
                                title = '')

sub <- subplot(rate_output[[1]], rate_output[[2]]) %>% layout(title = 'Rate per 10,000 Patients for Asthma Over Time') %>% style(showlegend = FALSE, traces = 1:24)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
rate_output[[3]]


```

## Hypertension
```{r}

rate_output <- fot_euclidean_viz(process_output = rate_euclidean,
                                output_var = 'incidence_rate',
                                filter_variable = 'hypertension',
                                title = '')

sub <- subplot(rate_output[[1]], rate_output[[2]]) %>% layout(title = 'Rate per 10,000 Patients for Hypertension Over Time') %>% style(showlegend = FALSE, traces = 1:24)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
rate_output[[3]]


```

## Respiratory Infection
```{r}

rate_output <- fot_euclidean_viz(process_output = rate_euclidean,
                                output_var = 'incidence_rate',
                                filter_variable = 'respiratory_infection',
                                title = '')

sub <- subplot(rate_output[[1]], rate_output[[2]]) %>% layout(title = 'Rate per 10,000 Patients for Respiratory Infection Over Time') %>% style(showlegend = FALSE, traces = 1:24)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
rate_output[[3]]


```

## Emergency Visits
```{r}

rate_output <- fot_euclidean_viz(process_output = rate_euclidean,
                                output_var = 'incidence_rate',
                                filter_variable = 'emergency_visits',
                                title = '')

sub <- subplot(rate_output[[1]], rate_output[[2]]) %>% layout(title = 'Rate per 10,000 Patients for Emergency Visits Over Time') %>% style(showlegend = FALSE, traces = 1:24)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
rate_output[[3]]


```

## Emergency Visit Vitals
```{r}


rate_output <- fot_euclidean_viz(process_output = rate_euclidean,
                                output_var = 'incidence_rate',
                                filter_variable = 'emergency_visit_vitals',
                                title = '')

sub <- subplot(rate_output[[1]], rate_output[[2]]) %>% layout(title = 'Rate per 10,000 Patients for Emergency Visit Vitals Over Time') %>% style(showlegend = FALSE, traces = 1:24)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
rate_output[[3]]


```

## Inpatient Administrations
```{r}


rate_output <- fot_euclidean_viz(process_output = rate_euclidean,
                                output_var = 'incidence_rate',
                                filter_variable = 'inpatient_administration',
                                title = '')

sub <- subplot(rate_output[[1]], rate_output[[2]]) %>% layout(title = 'Rate per 10,000 Patients for Inpatient Administrations Over Time') %>% style(showlegend = FALSE, traces = 1:24)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
rate_output[[3]]


```

## Inpatient Visits
```{r}


rate_output <- fot_euclidean_viz(process_output = rate_euclidean,
                                output_var = 'incidence_rate',
                                filter_variable = 'inpatient_visits',
                                title = '')

sub <- subplot(rate_output[[1]], rate_output[[2]]) %>% layout(title = 'Rate per 10,000 Patients for Inpatient Visits Over Time') %>% style(showlegend = FALSE, traces = 1:24)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
rate_output[[3]]


```

## Outpatient Procedures
```{r}


rate_output <- fot_euclidean_viz(process_output = rate_euclidean,
                                output_var = 'incidence_rate',
                                filter_variable = 'outpatient_procedure',
                                title = '')

sub <- subplot(rate_output[[1]], rate_output[[2]]) %>% layout(title = 'Rate per 10,000 Patients for Outpatient Procedures Over Time') %>% style(showlegend = FALSE, traces = 1:24)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
rate_output[[3]]


```

## Outpatient Visits
```{r}


rate_output <- fot_euclidean_viz(process_output = rate_euclidean,
                                output_var = 'incidence_rate',
                                filter_variable = 'outpatient_visits',
                                title = '')

sub <- subplot(rate_output[[1]], rate_output[[2]]) %>% layout(title = 'Rate per 10,000 Patients for Outpatient Visits Over Time') %>% style(showlegend = FALSE, traces = 1:24)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
rate_output[[3]]


```

# {-}

